%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{bold-extra}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.08003pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Arman Lalani} \\ \vspace{1pt}
    \small +91-7977231758 $|$ \href{mailto:armanlalani5@gmail.com}{\underline{armanlalani5@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/armanlalani}{\underline{linkedin.com/in/armanlalani}} $|$
    \href{https://github.com/armanlalani}{\underline{github.com/armanlalani}} $|$
    \href{https://www.armanlalani.com}{\underline{armanlalani.com/}}

\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dwarkadas J Sanghvi College of Engineering, Mumbai University}{2021}
      {Bachelor of Engineering (B.E.) $|$ 8.7 CGPA}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Associate}{June 2025 -- Present}
      {Institutional Shareholder Services}{Mumbai}
      \resumeItemListStart
        \resumeItem{Built a dynamic Field Mapping UI from scratch in React to transform arbitrary Excel uploads into structured, pipeline-ready data, handling header normalization, validation feedback, and error exports.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Fullstack Engineer}{June 2021 -- May 2025}
      {Tata Consultancy Services}{Mumbai}
      \resumeItemListStart
        \resumeItem{\emph{Collaborated with over 3 clients} to gather requirements, design prototypes, and implement final solutions in React based on feedback.}
        \resumeItem{Designed and implemented a scheduling feature that improved operational efficiency by 30\% for upcoming activities over the next 7 days.}
        \resumeItem{Created dynamic charts and graphs to visualize critical machine parameters, ensuring real-time data visibility and improving response times by 25\%.}
        \resumeItem{Authored comprehensive React unit test cases to maintain 95\%+ test coverage, maintaining reliability and performance.}
        \resumeItem{Provided ongoing support for the application, troubleshooting issues and ensuring system stability for over 500 end users.}
        \resumeItem{Resolved 10+ cloud vulnerabilities in AWS Lambdas by using AWS Secrets, enhancing data security and compliance.}
        \resumeItem{Played a key role in replicating and verifying 20+ APIs during database migration, ensuring data consistency through Postman test cases.}
        \resumeItem{Built an export functionality that allowed users to download actionable insights in Excel format, increasing report accessibility by 40\%.}
        \resumeItem{Delivered monthly presentations to stakeholders on project updates and technical progress.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Real-Time Manufacturing Analytics Platform} $|$ \emph{React, Redux, React Router, Node.js, Highcharts, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Developed a comprehensive analytics platform that delivered real-time insights into manufacturing operations, enhancing decisionmaking through interactive dashboards.}
            \resumeItem{Implemented a filter feature to display only relevant sensor values, improving the user experience for live monitoring.}
            \resumeItem{Created customized time series and bar charts to display production and machine performance data, enhancing visual analytics.}
            \resumeItem{Integrated a shop floor layout view with location-specific machine data, enabling users to track key performance indicators effectively.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Typescript, HTML/CSS, SQL} \\
     \textbf{Libraries \& Frameworks}{: React, Node.js, Redux, React Router, Jest, Enzyme, Material-UI, Tailwind, SASS, LESS, Git, Restful APIs, Webpack, NPM, Babel, JSON} \\
     \textbf{Other Skills}{: Responsive Web Design, Data Structures and Algorithms, Web Performance Optimization, Frontend Development, SonarQube, Technical Development} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
